High performance computing for global optimization problems

### 2018-08-20 2018/ITNT/ITNT2018.tex

>>>>

\bibitem{Kovartsev2017}
Kovartsev A N 2017 \textit{Computer Optics} \textbf{41(1)} 118--125 (In Russ.)

\bibitem{Golovashkin2016}
Malysheva S A and Golovashkin D L 2016 \textit{Computer Optics} \textbf{40(2)} 179--187 (In Russ.)

\bibitem{Golovashkin2017}
Vorotnikova D G and Golovashkin D L 2017 \textit{Computer Optics} \textbf{41(1)} 134--138 (In Russ.)
